On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/manuscript.tex
addressed comment on manuscript

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where coverage rates of were greater for stronger dependences 
regardless of the sign, coverage rates seem to be greater only for stronger 
negative
dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the 
percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence 
due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

\jy{This is for our method. Some percentile-based CIs may have coverage
  approaching zero, right?}
Although
we have only used serial dependences as strong as 0.4, we have established the 
trends as $|\phi|$ gets larger. When estimating $\mu$, we expect coverage rates 
to decrease as
$\phi$ approaches 1 --- as $\phi$ approaches -1, we may observe increased 
over-coverage. When estimating the standard deviation, we expect a larger sample 
size to
be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
a marginal normal distribution, we 
expect a larger sample size to be necessary as $|\phi|$ approaches 0. However, 
for a marginal exponential distribution, we expect coverage rates of the 
first-order autocorrelation to 
respond
to stronger dependences in a trend similar to that of coverage rates of~$\mu$.

>>>>

It appears that a greater sample size is generally required for the bootstrap
CIs to cover the mean and standard deviation parameters in the exponential
margin case than in the normal margin case. In contrast to the marginal normal
distribution, where standard normal, Student's $t$, and 
recentered percentile CI coverage rates were greater for stronger dependences 
regardless of the sign, coverage rates for these CIs seem to be greater only for 
stronger 
negative
dependencies and lesser for stronger positive dependences. 
\mc{What could be an explanation for this?}
However, the other 
trends 
and patterns
discussed in the main text regarding the performance of various methods and
diverse parameters remain consistent. For example, Student's $t$ confidence
intervals still exhibit higher coverage rates in comparison to alternative
methods. Performance continues to be more favorable when temporal dependence is
negative rather than positive. Of particular significance, the 
percentile, BC,
and BCA confidence intervals still display a decline in coverage accuracy for
the lag-1 autocorrelation coefficient as sample size increases as demonstrated
in Figure~\ref{fig:eri}. Both the percentile and BC intervals persist in
manifesting the same bias issue. On the other hand, the recentered percentile
confidence interval continues to be effective in estimating the temporal 
dependence 
due to the
inherent unbiasedness of the original point estimator. In sum, 
for the most part, the findings for
series that are marginally exponentially distributed closely mirror those
attained for series that are marginally normally distributed.

@@

\jy{This is for our method. Some percentile-based CIs may have coverage
  approaching zero, right?}
\mc{addressed}

Although
we have only used serial dependences as strong as 0.4, we have established the 
trends as $|\phi|$ gets larger. When estimating $\mu$, we expect coverage rates 
to decrease as
$\phi$ approaches 1 --- as $\phi$ approaches -1, we may observe increased 
over-coverage. When estimating the standard deviation, we expect a larger sample 
size to
be necessary as $|\phi|$ gets closer to 1. Lastly, when estimating $\phi$ for
a marginal normal distribution, we 
expect a larger sample size to be necessary as $|\phi|$ approaches 0, assuming
standard normal, Student's $t$, or 
recentered percentile CIs are used. However, 
when estimating the first-order autocorrelation of a marginal exponential 
distribution using the same methods, we expect coverage rates to 
respond
to stronger dependences in a trend similar to that of coverage rates of~$\mu$. 
We expect other percentile-based CIs, which are already inadequate for 
relatively weak
dependence structures, to perform even worse as $|\phi|$ approaches 1.
